Compare internal vs pooled references: SCPCP000015

### 2025-06-03 analyses/infercnv-consensus-cell-type/exploratory-notebooks/03_ewings-pooled-internal.Rmd
Apply suggestions from code review
Co-authored-by: Ally Hawkins <54039191+allyhawkins@users.noreply.github.com>

For several samples in `SCPCP000015`, we were able to run `inferCNV` with a so-called "internal" normal reference, where normal cells were taken only from the library being analyzed and were not pooled across all libraries.
The goal of this notebook is to directly compared results from internal references with their pooled counterparts to assess if there is evidence that the pooled reference strategy improves tumor/normal classification.

@@

* For all three libraries we were able to directly compare internal and pooled references for, the pooled reference appears to do either a similar or slightly a better job separating normal and tumor cells compared to the internal reference.
* There is no obvious inference where using a pooled reference appears _worse_ than using a pooled reference.
* Similar to previous observations we've made, the `endo` reference (either pooled or internal) shows improved separation between tumor and normal compared to references containing `immune` cells.
* Notably, `SCPCL001112` is a much smaller library than `SCPCL000822` and `SCPCL000824`, and we see evidence here that using a pooled reference dramatically improves separation between tumor and normal.

>>>>

For several samples in `SCPCP000015`, we were able to run `inferCNV` with a so-called "internal" normal reference, where normal cells were taken only from the library being analyzed and were not pooled across all libraries.
The goal of this notebook is to directly compare results from internal references with their pooled counterparts to assess if there is evidence that the pooled reference strategy improves tumor/normal classification.

@@

* For all three libraries we were able to directly compare internal and pooled references for, the pooled reference appears to do either a similar or slightly a better job separating normal and tumor cells compared to the internal reference.
* There is no obvious inference where using a pooled reference appears _worse_ than using an internal reference.
* Similar to previous observations we've made, the `endo` reference (either pooled or internal) shows improved separation between tumor and normal compared to references containing `immune` cells.
* Notably, `SCPCL001112` is a much smaller library than `SCPCL000822` and `SCPCL000824`, and we see evidence here that using a pooled reference dramatically improves separation between tumor and normal.
